Forecasting biodiversity in breeding birds using best practices

### 2017-12-09 manuscript/draft.Rmd

Despite the emerging interest in forecasting species richness and other aspects
of biodiversity [@jetz2007; @thuiller2011], little is known about how
effectively we can anticipate these dynamics. This is due in part to the long
time scales over which many ecological forecasts are applied [and the resulting
difficulty in assessing whether the predicted changes occurred; @dietze2016].
What we do know comes from a small number of hindcasting studies, where models
are built using data on species occurrence and richness from the past and
evaluated on their ability to predict contemporary patterns [e.g., @algar2009;
@distler2015]. These studies are a valuable first step, but lack several
components that are important for developing forecasting models with high
predictive accuracy, and for understanding how well different methods can
predict the future. These "best practices" for effective forecasting and
evaluation (Box 1) broadly involve: 1) expanding the use of data to include
biological and environmental time-series [@tredennick2016]; 2) accounting for
uncertainty in observations and processes, [@harris2015; @yu2010]; and 3)
conducting meaningful evaluations of the forecasts by hindcasting, archiving
short-term forecasts, and comparing forecasts to baselines to determine whether
the forecasts are more accurate than assuming the system is basically static
[@perretti2013].

>>>>

Despite the emerging interest in forecasting species richness and other aspects
of biodiversity [@jetz2007; @thuiller2011], little is known about how
effectively we can anticipate these dynamics. This is due in part to the long
time scales over which many ecological forecasts are applied [and the resulting
difficulty in assessing whether the predicted changes occurred; @dietze2016].
What we do know comes from a small number of hindcasting studies, where models
are built from different time periods and evaluated on their ability to predict
biodiversity patterns in contemporary [@algar2009; @distler2015] or historic
[@maguire2016; @blois2013] periods not used for model fitting. These studies are
a valuable first step, but lack several components that are important for
developing forecasting models with high predictive accuracy, and for
understanding how well different methods can predict the future. These "best
practices" for effective forecasting and evaluation (Box 1) broadly involve: 1)
expanding the use of data to include biological and environmental time-series
[@tredennick2016]; 2) accounting for uncertainty in observations and processes,
[@harris2015; @yu2010]; and 3) conducting meaningful evaluations of the
forecasts by hindcasting, archiving short-term forecasts, and comparing
forecasts to baselines to determine whether the forecasts are more accurate than
assuming the system is basically static [@perretti2013].
